What We Eval in the Shadows

### 2021-08-11 paper/main.tex
Fix graph

\begin{lstlisting}
 > e <- parse(text = "a ; b")
 > e[[2]] <- quote(c)
 > eval(e)
\end{lstlisting}

@@

\begin{figure}[h]
	\centering
	\begin{tikzpicture}[
		every node/.style={draw, rounded corners, fill=LightGray, text width = 2cm, align = center}
		]
		\node (E) at (2,0) {\c{eval(e)}};
		\node[text width = 3cm] (CA) at (2, 1.5) {\c{[[<-(e, 2, quote(c))}};
		\node (Q) at (4, 3) {\c{quote(c)}};
		\node[text width = 4cm] (A) at (0, 3) {\c{e <- parse(text = "a ; b"}};
		\node[text width = 3cm] (P) at (0, 4.5) {\c{parse(text = "a ; b"}};

		\draw[->, >=latex] (E) -- (CA);
		\draw[->, >=latex] (CA) -- (Q);
		\draw[->, >=latex] (CA) -- (A);
		\draw[->, >=latex] (A) -- (P);
	\end{tikzpicture}
\caption{Provenance} \label{fig:provgraph}
\end{figure}

>>>>

\begin{lstlisting}
 > e <- parse(text = "a;b")
 > e[[2]] <- quote(c)
 > eval(e)
\end{lstlisting}

@@

\begin{figure}[h]
	\centering
	\begin{tikzpicture}[
		every node/.style={draw, rounded corners, fill=LightGray, text width = 2cm, align = center}
		]
		\node (E) at (2,0) {\c{eval(e)}};
		\node[text width = 3cm] (CA) at (2, 1.5) {\c{e[[2]] <-quote(c)}};
		\node (Q) at (4, 3) {\c{quote(c)}};
		\node[text width = 4cm] (A) at (0, 3) {\c{e <- parse(text = "a;b")}};
		\node[text width = 3cm] (P) at (0, 4.5) {\c{parse(text = "a;b")}};

		\draw[<-, >=latex] (E) -- (CA);
		\draw[<-, >=latex] (CA) -- (Q);
		\draw[<-, >=latex] (CA) -- (A);
		\draw[<-, >=latex] (A) -- (P);
	\end{tikzpicture}
\caption{Provenance} \label{fig:provgraph}
\end{figure}
